Fast and exact visibility on digitized shapes and application to saliency-aware normal estimation

### 2025-04-22 DGMM2025/paper.tex
accept introduction and rework graph of mean distance as of gridstep

    \deleted[id=JO]{
    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
    }

    \deleted[id=JO]{
    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
    }

    \deleted[id=JO]{
      Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
    }

    \deleted[id=JO]{
      The remainder of this paper is structured as follows.
    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
    }

@@

                \draw (0,0) node at (-0.25,1.75) {V};
            \end{tikzpicture}\\
            \hline
            \multicolumn{2}{c}{
                \begin{tikzpicture}[scale=0.75]
                    \foreach \y in {0,0.5,...,12.5} {
                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
                    }
                    \foreach \y in {0,2.5,...,12.5} {
                        \draw[blue] (-7,\y) -- (11.25,\y);
                    }

@@

    \pgfplotsset{width=13cm}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Mean distance},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                    mark=square,
                ]
                coordinates {
                    (1,5.76973)(0.875,6.03836)(0.75,6.22426)(0.625,6.39012)(0.5,6.51014)(0.375,6.63571)(0.25,6.68132)
                };
                \addlegendentry{sphere9 radius 10}
                \addplot[
                    color=red,
                    mark=square,
                ]
                coordinates {
                    (1,5.91022)(0.875,6.10641)(0.75,6.14175)(0.625,6.20202)(0.5,6.28637)(0.375,6.44418)(0.25,6.56938)
                };
                \addlegendentry{goursat radius 10}
                \addplot[
                    color=red,
                    mark=triangle,
                ]
                coordinates {
                    (1,9.04228)(0.875,10.1319)(0.75,10.2837)(0.625,10.6125)(0.5,10.8969)(0.375,11.3186)(0.25,11.8382)
                };
                \addlegendentry{radius 20}
                \addplot[
                    color=red,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,9.22083)(0.875,10.6476)(0.75,11.5976)(0.625,12.7428)(0.5,13.9534)(0.375,14.73)(0.25,15.8425)
                };
                \addlegendentry{radius 30}
                \addplot[
                    color=violet,
                    mark=square,
                ]
                coordinates {
                    (1,5.36873)(0.875,5.43148)(0.75,5.47206)(0.625,5.67227)(0.5,5.81554)(0.375,6.03961)(0.25,6.31671)
                };
                \addlegendentry{torus}
                \addplot[
                    color=violet,
                    mark=triangle,
                ]
                coordinates {
                    (1,6.42158)(0.875,6.36929)(0.75,6.94675)(0.625,7.65529)(0.5,8.65652)(0.375,9.05402)(0.25,10.0784)
                };
                \addplot[
                    color=violet,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,6.44119)(0.875,6.43563)(0.75,7.00852)(0.625,7.71613)(0.5,9.1544)(0.375,9.84299)(0.25,12.241)
                };
            \end{axis}
        \end{tikzpicture}
        \caption{Mean Visibility Distance as a Function of Grid Resolution}
    \end{figure}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Duration (s)},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                    mark=square,
                ]
                coordinates {
                    (1,0.513)(0.875,0.585)(0.75,0.897)(0.625,1.401)(0.5,2.441)(0.375,4.664)(0.25,11.420)
                };
                \addlegendentry{sphere9 radius 10}
                \addplot[
                    color=red,
                    mark=square,
                ]
                coordinates {
                    (1,0.440)(0.875,0.665)(0.75,0.823)(0.625,1.428)(0.5,2.463)(0.375,4.697)(0.25,11.766)
                };
                \addlegendentry{goursat radius 10}
                \addplot[
                    color=red,
                    mark=triangle,
                ]
                coordinates {
                    (1,1.389)(0.875,2.567)(0.75,3.661)(0.625,7.123)(0.5,13.881)(0.375,28.913)(0.25,77.360)
                };
                \addlegendentry{radius 20}
                \addplot[
                    color=red,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,2.172)(0.875,3.747)(0.75,5.565)(0.625,13.180)(0.5,33.088)(0.375,80.584)(0.25,240.546)
                };
                \addlegendentry{radius 30}
                \addplot[
                    color=violet,
                    mark=square,
                ]
                coordinates {
                    (1,0.057)(0.875,0.081)(0.75,0.097)(0.625,0.197)(0.5,0.330)(0.375,0.800)(0.25,2.253)
                };
                \addlegendentry{torus}
                \addplot[
                    color=violet,
                    mark=triangle,
                ]
                coordinates {
                    (1,0.248)(0.875,0.294)(0.75,0.339)(0.625,0.620)(0.5,1.110)(0.375,2.643)(0.25,9.369)
                };
                \addplot[
                    color=violet,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,0.837)(0.875,0.880)(0.75,0.942)(0.625,1.316)(0.5,2.142)(0.375,5.046)(0.25,20.418)
                };
            \end{axis}
        \end{tikzpicture}
        \caption{Computation Time of Visibility as a Function of Grid Resolution}
    \end{figure}

>>>>

%    \deleted[id=JO]{
%    Visibility is a fundamental concept in computational geometry and digital topology, with applications ranging from computer vision to geometric modeling and computer graphics.
%    In this work, we explore visibility through the lens of chord tangency, introducing a novel approach that builds on discrete geometric structures.
%    Our framework leverages the discrete setting of and cell complexes, providing a rigorous foundation for analyzing visibility properties in digital spaces.
%    }
%
%
%    \deleted[id=JO]{
%    We recall essential definitions from previous works, particularly the notions of cell complexes and the star operator as formalized in~\cite{lachaud:2021-dgmm} and~\cite{lachaud:2022-jmiv}.
%    The integer grid serves as our primary space of study, where geometric structures are discretized using cell complexes.
%    A cell complex is a decomposition of space into elementary units (vertices, edges, faces, and higher-dimensional counterparts) forming a combinatorial representation of geometric objects.
%    The star of a cell, as defined in these works, consists of all higher-dimensional cells that contain it, a crucial concept for analyzing local neighborhoods and connectivity.
%    }
%
%    \deleted[id=JO]{
%      Building on these foundations, our study focuses on visibility as determined by the tangency of chords in discrete geometry.
%    We define and analyze how visibility relationships emerge in this context and investigate their combinatorial and topological implications.
%    This approach provides a new perspective on discrete visibility, offering potential applications in digital imaging, surface reconstruction, and computational topology.
%    }
%
%    \deleted[id=JO]{
%      The remainder of this paper is structured as follows.
%    In Section 2, we formalize the concept of chord tangency and its role in visibility analysis.
%    Section 3 enters into the usage of integer intervals intersections to quickly scan the figure in order to recover this visibiltiy.
%    Section 4 presents our main results, using this visibility to compute normals using the CNC estimator~\cite{lachaud:2022-dcg}.
%    Finally, Section 5 concludes with some other applications of integer intervals intersections in the field.
%    }

@@

                \draw (0,0) node at (-0.25,1.75) {V};
            \end{tikzpicture} \\
            \hline
            \multicolumn{2}{c}{
                \begin{tikzpicture}[scale=0.75]
                    \foreach \y in {0,0.5,...,12.5} {
                        \draw[thin, lightgray] (-1.25,\y) -- (11.25,\y);
                    }
                    \foreach \y in {0,2.5,...,12.5} {
                        \draw[blue] (-7,\y) -- (11.25,\y);
                    }

@@

    \pgfplotsset{width=13cm}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Mean distance},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymax=50,
                ymode=log,
                xmode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                ] coordinates {
                    (0.25,3.97418)(0.375,3.00921)(0.5,2.85702)(0.625,2.34448)(0.75,1.85023)(0.875,2.16868)(1.0,1.85023)
                };
                \addlegendentry{sphere1}
                \addplot[
                    color=red,
                ] coordinates {
                    (1,8.90781)(0.875,10.2845)(0.75,11.3734)(0.625,12.5062)(0.5,14.0867)(0.375,16.6192)(0.25,19.6747)
                };
                \addlegendentry{goursat}
                \addplot[
                    color=violet,
                ] coordinates {
                    (0.25,12.3975)(0.375,9.41303)(0.5,8.69558)(0.625,7.37667)(0.75,6.82131)(0.875,6.05735)(1,6.33877)
                };
                \addlegendentry{torus}
                \addplot[
                    color=MyGreen,
                ] coordinates {
                    (0.25,10.8007)(0.375,8.69514)(0.5,7.26074)(0.625,6.2309)(0.75,5.6897)(0.875,5.28197)(1,4.96098)
                };
                \addlegendentry{leopold}
                \addplot[
                    color=yellow!80!black,
                ] coordinates {
                    (0.25,18.2339)(0.375,14.6475)(0.5,12.3618)(0.625,9.55647)(0.75,9.83208)(0.875,7.51861)(1,7.99732)
                };
                \addlegendentry{rcube}
                \addplot [
                    color=black,
                    thick,
                    domain=0.25:1,
                    samples=100,
                ] {x^(-0.5)};
                \addlegendentry{$\sqrt{h}=\sqrt{\frac{1}{x}}$}
            \end{axis}
        \end{tikzpicture}
        \caption{Mean Visibility Distance as a Function of Grid Resolution}
        \label{fig:meanvisibility-gridstep}
    \end{figure}
    \begin{figure}
        \begin{tikzpicture}
            \centering
            \begin{axis}[
                xlabel={Gridstep},
                x dir=reverse,
                ylabel={Duration (s)},
                legend pos=north west,
                ymajorgrids=true,
                grid style=dashed,
                ymode=log,
                log ticks with fixed point,
            ]

                \addplot[
                    color=cyan,
                    mark=square,
                ]
                coordinates {
                    (1,0.513)(0.875,0.585)(0.75,0.897)(0.625,1.401)(0.5,2.441)(0.375,4.664)(0.25,11.420)
                };
                \addlegendentry{sphere9 radius 10}
                \addplot[
                    color=red,
                    mark=square,
                ]
                coordinates {
                    (1,0.440)(0.875,0.665)(0.75,0.823)(0.625,1.428)(0.5,2.463)(0.375,4.697)(0.25,11.766)
                };
                \addlegendentry{goursat radius 10}
                \addplot[
                    color=red,
                    mark=triangle,
                ]
                coordinates {
                    (1,1.389)(0.875,2.567)(0.75,3.661)(0.625,7.123)(0.5,13.881)(0.375,28.913)(0.25,77.360)
                };
                \addlegendentry{radius 20}
                \addplot[
                    color=red,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,2.172)(0.875,3.747)(0.75,5.565)(0.625,13.180)(0.5,33.088)(0.375,80.584)(0.25,240.546)
                };
                \addlegendentry{radius 30}
                \addplot[
                    color=violet,
                    mark=square,
                ]
                coordinates {
                    (1,0.057)(0.875,0.081)(0.75,0.097)(0.625,0.197)(0.5,0.330)(0.375,0.800)(0.25,2.253)
                };
                \addlegendentry{torus}
                \addplot[
                    color=violet,
                    mark=triangle,
                ]
                coordinates {
                    (1,0.248)(0.875,0.294)(0.75,0.339)(0.625,0.620)(0.5,1.110)(0.375,2.643)(0.25,9.369)
                };
                \addplot[
                    color=violet,
                    mark=halfcircle,
                ]
                coordinates {
                    (1,0.837)(0.875,0.880)(0.75,0.942)(0.625,1.316)(0.5,2.142)(0.375,5.046)(0.25,20.418)
                };
            \end{axis}
        \end{tikzpicture}
        \caption{Computation Time of Visibility as a Function of Grid Resolution}
        \label{fig:meanvisibility-computationComplexity}
    \end{figure}
